---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rrCoho

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/rrCoho)](https://CRAN.R-project.org/package=rrCoho)
<!-- badges: end -->

Functions associated with 

  - data compilation
    - escapements
      - counts from hatchery facilities
      - estimates from in-situ spawning and other surveys
    - catches
      - commercial net reporting
      - estimates from recreational harvest and encounters
    - code wire tags
  - assignment to relevant stock units
  - outputs

## Installation

You can install the development version of rrCoho from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("FRAMverse/rrCoho")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(rrCoho)
## basic example code
```

