---
title: "rrCoho overview"
author: "Dan.Auerbach@dfw.wa.gov"
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
output: 
  bookdown::html_document2:
    self_contained: true
    fig_caption: yes
    theme: flatly
    toc: yes
    toc_depth: 3
    toc_float: yes
    code_folding: hide
---
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = FALSE, warning = FALSE, message = FALSE, fig.width = 9, fig.height = 9)

library("tidyverse")
#library("odbc"); library("DBI")
library("gt")

data_in <- list()

# params:
#   fp_escp:
#   fp_hvst:
```

# Established lookups

```{r read_rrterm_mdb}
db <- "O:/code/coho/rrterm/CohoRR_4_CoManagerReview_020221/RRT_CO_2019-10_2021-02-02.mdb"
db_con <- DBI::dbConnect(drv = odbc::odbc(), .connection_string = paste0("Driver={Microsoft Access Driver (*.mdb, *.accdb)};DBQ=", db, ";"))

rr <- list(
  lu_pr = "PR_Data", #stock "production regions"
  lu_mu = "MU_Data", #stock "management units" within production regions
  lu_ca = "CA_Data", #"catch areas"
  lu_ca_mu = "CA_MU_Table", #cross-ref
  
  pef = "MU_Local_PEF", #what makes field "Local_PEF" and where is it used?
  qval = "MU_PR_Qval", #what is field "Qvalue" and where is it used?
  hr_scaler = "MU_HR_Scaler", #what makes field "HR_Value" and where is it used?
  cwt = "CWT_Rec", #recoveries of CWTs indexed by CA and MU_Short_Name but not PR & PR_MU
  
  hvst = "CA_Catch",
  escp = "MU_Escapement",
  
  run_calc_saved = "Run_Calc_Saved" #appears to be output matching xlsx
) |> 
  map(~collect(tbl(db_con, .x)))

DBI::dbDisconnect(db_con)

```

Move these into `data/` via `use_data()`? 

```{r}
rr$lu_mu

rr$lu_ca |> 
  select(FisheryID = FRAM_CA_Number, CA_Number, CA_Short_Name, CWT_Flag, Cat_Flag, Type_Calc) |>
  write_csv("lu_rrterm_CA_FRAM.csv")

rr$lu_ca_mu

```

# Escapement

depends on current format of *fram_coho_escapement_YEAR.xlsx* file

reads 'dataset' sheet and wrangles to 'RRTerm' summarization by PR + PR_MU

easily modified if replacement maintains comparable "view" of PR & PR_MU fields per escapement estimate value

but underlying compilation of values in 'dataset' only partially scriptable; see fram_coho_escapement_2022.R for hatchery queries etc.

```{r}
data_in$escp <- readxl::read_excel(
  path = "copy_of_fram_coho_escapement_2022.xlsx",
  sheet = "dataset"
)|> 
  group_by(year, PR = RRTerm_PR, PR_MU = RRTerm_PR_MU) |> 
  summarise(escp = sum(escp_val, na.rm = T)) 

data_in$escp |> filter(year == 2019)

```

# Catches

Hopefully some/all of this gets revised to query the combined data source project from Eric K/Brodie/others?

## Commercial: FishTix

## Commercial: TOCAS

## Recreational: CRC

```{r read_crc_coho}
#readRDS("T:/DFW-Salmon Mgmt Modeling Team - General/Catch datasets/CRC/d_spt_hvst_est_20220302.rds")

db_crc <- "T:/DFW-Salmon Mgmt Modeling Team - General/Catch datasets/CRC/Sport Harvest Estimates 20220302.mdb"
db_con <- dbConnect(drv = odbc(), .connection_string = paste0("Driver={Microsoft Access Driver (*.mdb, *.accdb)};DBQ=",db_crc,";"))

crc_coho <- dplyr::left_join(
  dplyr::collect(dplyr::tbl(db_con, "Catch")) |> 
    dplyr::mutate(dplyr::across(ends_with("Date"), ~as.Date(., format = "%m/%d/%Y"))) 
  , 
  dplyr::collect(dplyr::tbl(db_con, "Area"))
  ,
  by = "AreaID") |> 
  dplyr::rename_with(.fn = tolower) |> 
  filter(species == "Coho", areacode != "192") |> 
  mutate(
    area_code = str_pad(areacode, width = 2, pad = "0"),
    #confirmed MB comment that 9 records in 2007 & 2008 were NA but all first week of Jan
    #assign from catchperiodstartdate
    catchstatmonth = if_else(is.na(catchstatmonth), as.integer(format(catchperiodstartdate, '%m')), catchstatmonth)
    ) |>
  group_by(area_code, areaname, year = catchyear, catchstatmonth) |> 
  summarise(catchest = sum(catchest), .groups = "drop") |> 
  mutate(
    m = factor(month.abb[catchstatmonth], levels = month.abb),
    ts = case_when(
      m %in% month.abb[1:6] ~ 1,
      m == "Jul" ~ 2,
      m == "Aug" ~ 3,
      m == "Sep" ~ 4,
      m %in% month.abb[10:12] ~ 5)
    )

dbDisconnect(db_con)

```

**Notes**

> #MB Because use of this data is often to utilize a catch number if it exists, by default data should be non-zero.
#Thus, I'm going to remove these zero values.  Not in all analysis or uses will it be appropriate to remove these!

This seems unnecessary/ill-advised. Zeros would either be aggregated in sums or meaningful if not data errors.

> #MB Also going to remove data with an Unknown (=192) AreaCode (no existing records with Invalid (=193))

Persisted, and/but could/should also be handled via LU on desired CAs? `rr$lu_ca_mu`

> #Generate coho FRAM time steps from Month
# 1=Jan-June, 2=July, 3=Aug, 4=Sept, 5=Oct-Dec

Based on `catchstatmonth` ignoring start/end dates outside single month

Persisted CRC~FRAM LU as assigned.

But need? 
>#To generate ouput of landings data for use in old RRTerm for Coho RR. Use a translation table to combine and translate FRAM_FisheryID to OldRR CA_Number - ONLY includes Strait Juan de Fuca + Puget Sound!
fisheryRR <- read.csv( "C:/Users/mbellman/Documents/Run_Reconstruction/Coho/MB_Draft_2020/ReferenceFiles_4Rcode/FRAMFisheryID_2_RRTermCANumber.csv", header=T)

```{r crc_coho_assign_fram_id}
crc_coho <- crc_coho |> 
  mutate(
    FisheryID = case_when(
      area_code == "01" ~ 33, #A1-Ast Spt
      area_code == "02" ~ 37, #Area 2 Spt
      area_code == "03" ~ 40, #Area 3 Spt
      area_code == "04" ~ 41, #Area 4 Spt
      area_code == "21" ~ 45, #Willpa Spt, marine only
      area_code %in% c(
        '305','375',
        '377','378','379',
        '382','384','389',
        '390','422','424') ~ 46,  #Wlp Tb Spt, freshwater only
      area_code == "22" ~ 48, #GryHbr Spt
      area_code %in% c('342','367') ~ 49, #SGryHb Spt, (342=Elk River, 367=Johns River)
      area_code %in% c('358','361','362') ~ 51,  #Hump R Spt, freshwater only
      area_code %in% c(
        '315','317','319',
        '325','333','370',
        '419','706','321') ~ 54, #Chehal Spt, freshwater only (?including Quigg Lake=370)
      #MarleneB: FisheryID = 58,59,60,61 - roll into FisheryID=54, to align with how pre-season inputs are calculated
      area_code == 337 ~ 54, #Wynoch Spt FisheryID 58
      area_code == 355 ~ 54, #Hoquam Spt FisheryID 59
      area_code == 335 ~ 54, #Wishkh Spt FisheryID 60
      area_code %in% c('329','331') ~ 54, #Satsop Spt FisheryID 61
      area_code %in% c(
        '327','410','412','408') ~ 62,  #Quin R Spt; no FRAM BP
      area_code == 394 ~ 65, #(Queets Spt)
      #MarleneB FisheryID = 66,67 - roll into 65, to align with how pre-season inputs are calculated
      area_code == 392 ~ 65, #Clrwtr Spt FisheryID 66
      area_code == 396 ~ 65, #Salm R Spt FisheryID 67
      area_code %in% c(
        '398','400',
        '402','404','406') ~ 70, #Quilly Spt
      area_code %in% c(
        '348','350','352') ~ 73, #Hoh R Spt
      #No FRAM BP for F76 Makah Tributary Sport
      #MarleneB: perhaps Big River (Clallam Co) = 386, Sooes River (Clallam Co) = 418, Waatch River = 420
      area_code %in% c(
        '782','822','772') ~ 89, #EJDF FWSpt no BP available
      area_code %in% c(
        '718','726','740',
        '752','768','810',
        '814','818','882') ~ 90, #WJDF FWSpt
      area_code == '05' ~ 91, #Area 5 Spt
      area_code == '06' ~ 92, #Area 6 Spt
      area_code == '07' ~ 93, #Area 7 Spt
      area_code %in% c('738','311') ~ 94, #Dung R Spt
      area_code == '742' ~ 95, #ElwhaR Spt
      
      #MarleneB: not included; 724-Dakotah Creek into 7A directly, 884-Whatcom Creek into 7B directly
      area_code %in% c(
        '788','790',
        '792','794','838') ~ 99, #Nook R Spt
      area_code == '816' ~ 100, #Samh R Spt
      area_code == '81' ~ 106, #Ar 8-1 Spt
      area_code == '09' ~ 107, #Area 9 Spt
      area_code %in% c(
        '824','825','826',
        '828','830','832') ~ 108, #Skag R Spt
      area_code == '82' ~ 115, #Ar 8-2 Spt
      area_code %in% c(
        '866','872','874','876') ~ 116,  #Stilg R Spt
      area_code %in% c(
        '840','844','846',
        '848','850','852',
        '858','860') ~ 117, #Snoh R Spt, including Wallace, Skykomish, Snoqualmie, Pilchuck
      area_code == '10' ~ 118, #Ar 10 Spt
      area_code == '746' ~ 127, #Duwm R Spt
      area_code %in% c(
        '712','760','762','764') ~ 128, #L WaSm Spt
      area_code == '11' ~ 129, #Ar 11 Spt
      area_code %in% c(
        '802','804','806','808') ~ 135, #Puyl R Spt
      area_code == '13' ~ 136, #Ar 13 Spt
      area_code %in% c(
        '708','714','720',
        '744','754','770',
        '774','776','778',
        '798','820') ~ 149, #13D-K TSpt
      area_code == '786' ~ 150, #Nisq R Spt
      area_code == '728' ~ 151, #Desc R Spt
      area_code == '12' ~ 152, #Ar 12 Spt
      area_code %in% c(
        '702','734','736','750') ~ 163, #1212B TSpt
      area_code %in% c('766','812') ~ 164, #12A Tb Spt
      area_code %in% c('732','878','880') ~ 165, #12C-D TSpt
      area_code %in% c('796','834','836') ~ 166 #Skok R Spt
    )
  )

#crc_coho |> filter(is.na(FisheryID)) |> count(area_code, areaname) |> arrange(area_code) |> print(n=100)

```

This appears to work to assign RRTerm CA?

```{r}
lu_fram_ca <- readr::read_csv("lu_rrterm_CA_FRAM.csv")

crc_coho |> 
  drop_na(FisheryID) |> 
  filter(year == 2019) |> 
  inner_join(lu_fram_ca, by = "FisheryID") |> 
  inner_join(rr$lu_ca_mu, by = "CA_Number")


```


# CWTs

# Assignment