---
title: "rrCoho overview"
author: "Dan.Auerbach@dfw.wa.gov"
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
output: 
  bookdown::html_document2:
    self_contained: true
    fig_caption: yes
    theme: flatly
    toc: yes
    toc_depth: 3
    toc_float: yes
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = FALSE, warning = FALSE, message = FALSE, fig.width = 9, fig.height = 9)

library("tidyverse")
library("gt")

library("framr")

lu <- list(
  crc_fram = as_tibble(framr::lu_coho_crc_fram),
  tocas_fram = as_tibble(framr::lu_coho_tocas_fram),
  
  fram_ca = readr::read_csv("lu_FRAM_CA.csv"),
  ca_pr_mu = readr::read_csv("lu_rrterm_CA_PR_MU.csv")
)

data_in <- list()

# params:
#   file_escp:
#     - target version of CoTC escapement compilation file? Not yet a function since just a simple readxl
#   file_crc:
#     - target sport harvest mdb; this can/should change if/when a directly query-able resource becomes available
#   file_tocas:
#     - target for TOCAS query dataset






mb20 <- list()
mb20$escp <- read_csv("O:/code/coho/rrterm/MB_Draft_2020/Data_ProcessingSteps/Escapement_Inputs/MU_Escapement_013122.csv")
mb20$crc <- read_csv("O:/code/coho/rrterm/MB_Draft_2020/Data_ProcessingSteps/Landings_Sport/RRTerm_CA_Catch_FinalInputSpt_RegularTS_012722.csv")
  #read_csv("O:/code/coho/rrterm/MB_Draft_2020/Data_ProcessingSteps/Landings_Commercial/")


```


https://fisheriesservices.nwifc.org/fram-model-runs/preseason-fram-model-preparation/salmon-run-reconstruction-puget-sound/

-CWT assignment is to FRAM units first
  - fishery via rec_loc_code
  - stock via ...? RMIS fields of some sort
-Fisheries sequential within PR?!? (turns out no)
-user choice to alter flagging for use of CWTs --> actually this is the "sequential" aspect, moving in from pre-terminal
  -MB codified ruleset for when to "turn-off"
-MSFs require "tricking" via small PEF (fishery-year specific based on regs) values of 0.0001
  -MB suggest improving this, perhaps via something like an MSF flag
  -this may have been the point at which 2006 Packer development stalled? Due to lack of marked-catch data 
-recall HC is copy-paste from regional Cindy Gray RR


# Established lookups

```{r read_rrterm_mdb, eval=FALSE}
db <- "O:/code/coho/rrterm/CohoRR_4_CoManagerReview_020221/RRT_CO_2019-10_2021-02-02.mdb"
db_con <- DBI::dbConnect(drv = odbc::odbc(), .connection_string = paste0("Driver={Microsoft Access Driver (*.mdb, *.accdb)};DBQ=", db, ";"))

rr <- list(
  lu_pr = "PR_Data", #stock "production regions"
  lu_mu = "MU_Data", #stock "management units" within production regions
  lu_ca = "CA_Data", #"catch areas"
  lu_ca_mu = "CA_MU_Table", #cross-ref
  
  pef = "MU_Local_PEF", #what makes field "Local_PEF" and where is it used?
  qval = "MU_PR_Qval", #what is field "Qvalue" and where is it used?
  hr_scaler = "MU_HR_Scaler", #what makes field "HR_Value" and where is it used?
  cwt = "CWT_Rec", #recoveries of CWTs indexed by CA and MU_Short_Name but not PR & PR_MU
  
  hvst = "CA_Catch",
  escp = "MU_Escapement",
  
  run_calc_saved = "Run_Calc_Saved" #appears to be output matching xlsx
) |> 
  map(~collect(tbl(db_con, .x)))

DBI::dbDisconnect(db_con)

```

```{r write_lu_csvs, eval=FALSE}
rr$lu_mu

# #mapping FRAM FisheryIDs to RRterm CA catch areas
# #now added MB FW/M RRTermType field to define which FRAM timesteps used in aggregation to annual
# rr$lu_ca |>
#   select(FisheryID = FRAM_CA_Number, CA_Number, CA_Short_Name, CWT_Flag, Cat_Flag, Type_Calc) |>
#   left_join(
#     read_csv("O:/code/coho/rrterm/MB_Draft_2020/ReferenceFiles_4Rcode/Fishery_CohoFRAM_wType_101018.csv") |>
#       select(FisheryID, RRTermType),
#     by = "FisheryID"
#   ) |>
#   write_csv("lu_FRAM_CA.csv")


# #mapping RRterm fishery CAs to stock PR+PR_MU
# #the key crosswalk to assign catches to associated stocks
# rr$lu_ca_mu |> 
#   mutate(PR_MU = paste(PR_Number, PR_MU_Number, sep = "_")) |> 
#   write_csv("lu_rrterm_CA_PR_MU.csv")

```

# Escapement

expects/relies on current format of *fram_coho_escapement_YEAR.xlsx* file

reads 'dataset' sheet and wrangles to 'RRTerm' summarization by PR + PR_MU

easily modified if replacement maintains comparable "view" of PR & PR_MU fields per escapement estimate value

but underlying compilation of values in 'dataset' only partially scriptable; see fram_coho_escapement_2022.R for hatchery queries etc.

```{r read_escp}
data_in$escp <- readxl::read_excel(
  path = "copy_of_fram_coho_escapement_2022.xlsx",
  sheet = "dataset"
)|> 
  group_by(year, RRTerm_PR, RRTerm_PR_MU) |> 
  summarise(escp = sum(escp_val, na.rm = T), .groups = "drop") |> 
  mutate(
    PR_MU = paste(RRTerm_PR, RRTerm_PR_MU, sep = "_"),
    across(c(year, escp), as.integer)
    )
```

Good agreement with what appears to be MB final "RRTerm input".

  - Willapa numbers updated 2/7/22 in course of WB forecast, after MB ran 1/31/22
  - Quilcene H, Makah H, Quin H values from Carrie Cook-Tabor; also "hoodsh"? But having placeholder 0s in template ensured these were not new/NA from my file
  - Elwha was a late-changing regional conversation; need to check exactly what was agreed final with Jenni W as DA may not have all emails

```{r compare_escp}
full_join(
  data_in$escp |> filter(year == 2020),
  mb20$escp,
  by = c("RRTerm_PR" = "PR_Number", "RRTerm_PR_MU" = "PR_MU_Number")
  ) |> 
  filter(is.na(escp) | is.na(Escapement) | abs(escp - Escapement) > 1)

```

# Catches

Hopefully some/all of this gets revised to query the combined data source ("HarvestCube") project from JohnChen/Eric K/Brodie?

## Recreational: CRC

```{r read_crc_coho}
#readRDS("T:/DFW-Salmon Mgmt Modeling Team - General/Catch datasets/CRC/d_spt_hvst_est_20220302.rds")

db_crc <- "T:/DFW-Salmon Mgmt Modeling Team - General/Catch datasets/CRC/Sport Harvest Estimates 20220302.mdb"
db_con <- DBI::dbConnect(drv = odbc::odbc(), .connection_string = paste0("Driver={Microsoft Access Driver (*.mdb, *.accdb)};DBQ=",db_crc,";"))

data_in$crc <- dplyr::left_join(
  dplyr::collect(dplyr::tbl(db_con, "Catch")) |> 
    dplyr::mutate(dplyr::across(ends_with("Date"), ~as.Date(., format = "%m/%d/%Y"))) 
  , 
  dplyr::collect(dplyr::tbl(db_con, "Area"))
  ,
  by = "AreaID") |> 
  dplyr::rename_with(.fn = tolower) |> 
  filter(species == "Coho", areacode != "192") |> 
  mutate(
    area_code = str_pad(areacode, width = 2, pad = "0"),
    #confirmed MB comment that 9 records in 2007 & 2008 were NA but all first week of Jan
    #assign from catchperiodstartdate
    catchstatmonth = if_else(is.na(catchstatmonth), as.integer(format(catchperiodstartdate, '%m')), catchstatmonth)
    ) |>
  group_by(area_code, areaname, year = catchyear, catchstatmonth) |> 
  summarise(catchest = sum(catchest), .groups = "drop") |> 
  mutate(
    m = factor(month.abb[catchstatmonth], levels = month.abb),
    ts = case_when(
      m %in% month.abb[1:6] ~ 1,
      m == "Jul" ~ 2,
      m == "Aug" ~ 3,
      m == "Sep" ~ 4,
      m %in% month.abb[10:12] ~ 5)
    )

DBI::dbDisconnect(db_con)

```

**Notes from CohoFRAM_PostSeasonwMZ_RR_SportFisheryInputs_111021.R**

> #MB Because use of this data is often to utilize a catch number if it exists, by default data should be non-zero.
#Thus, I'm going to remove these zero values.  Not in all analysis or uses will it be appropriate to remove these!

This seems unnecessary/ill-advised. Zeros would either be aggregated in sums or meaningful if not data errors.

> #MB Also going to remove data with an Unknown (=192) AreaCode (no existing records with Invalid (=193))

Persisted, and/but could/should also be handled via LU on desired CAs? `rr$lu_ca_mu`

> #Generate coho FRAM time steps from Month
# 1=Jan-June, 2=July, 3=Aug, 4=Sept, 5=Oct-Dec

Based on `catchstatmonth` ignoring start/end dates outside single month

Persisted CRC~FRAM LU as assigned. Migrated assignment to `framr::lu_coho_crc_fram`

```{r crc_assign_fram_id}
data_in$crc <- dplyr::left_join(
  data_in$crc,
  dplyr::select(lu$crc_fram, -FisheryID_alt),
  by = "area_code")
  #rrCoho::assign_fram_fishery_to_crc(data_in$crc)

##unassigned
#data_in$crc |> filter(is.na(FisheryID)) |> count(area_code, areaname) |> arrange(area_code) |> print(n=100)

```

Assign RRTerm CA from FRAM FisheryID

Seems catches only summed from FRAM timestep 3+4+5 FW or 4+5 Marine (Aug+Sep+Oct-Nov).

Seems undesirable to DA, but persisting per AHB. Apparently "dip-in" concerns.

Near exact agreement, differences almost certainly related to using newer CRC.

```{r compare_crc}
#maintaining FW 3+4+5, M 4+5 per AHB, but would prefer not to exclude pre-Aug catch on basis of 'dip in' concerns
#no idea how CWT_Flag, Cat_Flag, Type_Calc are used
data_in$crc |> 
  drop_na(FisheryID) |> 
  inner_join(lu$fram_ca, by = "FisheryID") |> 
  drop_na(RRTermType) |> 
  filter(ts > 2) |> 
  group_by(year, FisheryID, CA_Number, CA_Short_Name, CWT_Flag, Cat_Flag, Type_Calc, RRTermType, ts) |> 
  summarise(catchest = sum(catchest), .groups = "drop") |> 
  pivot_wider(names_from = ts, values_from = catchest, values_fill = 0) |> 
  mutate(
    catch = case_when(
      RRTermType == "FW" ~ `3` + `4` + `5`,
      RRTermType == "M" ~ `4` + `5`
    )
  ) |> 
  filter(year == 2020) |> 
  left_join(
    mb20$crc |> filter(Run_ID == 2020),
    by = "CA_Number"
  )

```


```{r}
  #when full set of catches associated to CAs, then associate stock units per fishery/CA
  inner_join(lu$ca_pr_mu, by = c("CA_Number", "CA_Short_Name")) |> 
  #and then escp, tocas, etc.
  inner_join(data_in$escp |> select(year, PR_MU, escp), by = c("year", "PR_MU")) |> 
  group_by(year, FisheryID, CA_Number) |> 
  mutate(
    pct_escp = escp / sum(escp),
    catchest_pct_escp = catchest * pct_escp
    ) |> 
  group_by(year, PR_MU, MU_Short_Name) |> 
  summarise(escp = first(escp), crc = sum(catchest_pct_escp), .groups = "drop")

```

## Commercial: TOCAS

**Notes from CohoFRAM_PostSeason_RR_CommCatchInputs_MB111221**

>#######################################################################################
#TO QUERY RAW DATA (http://access.nwifc.org/webapps/index.asp)
#In Tribal Online Accounting System (TOCAS) interface, the query is structured as follows:
>#Biological Reports
>#TOCAS/WAFT
#Breaks: SpeciesName, Fishery, Gear, GearName, Catch Area, Disposition, Landing Date, Tribe Name.
#Select - TOCAS Filled with WAFT Data
#Values:  Select - Units
#Criteria:
# Species Selected =  
# 004 - COHO
# 044 - COHO AQUACULTURE (Note: no results, but keep in query to see if any show-up....)
# (Do not include 874 - COHO EGGS)
# Tribes Selected = ALL
# Gears Selected = ALL
# Areas Selected = ALL
# Disposition Selected = ALL
# Dealers Selected = ALL
# 
# Begin Date = 01/01/1986,  End Date = 12/31/2020  (modify as needed)
#Save the raw data in a .csv file on your computer.


## Commercial: FishTicket

MB appears to have used TOCAS exclusively.

```{r ft_pull, eval=FALSE}
#con_ft <- assign connection here

#Not limited to PS commercial in FRAM - various ColR and coastal catches...
ft_pull <- inner_join(
  tbl(con_ft, dbplyr::in_schema(schema = "Reporting", table = "vFishTicketCat2")),
  tbl(con_ft, dbplyr::in_schema(schema = "Reporting", table = "vFishTicketDetailCat2"))
  , by = c("FishTicketID")
  ) |> 
  filter(
    ReleaseStatus == "Completed",
    MarketSpeciesCategoryName == "COHO",
    BatchYear >= 2015, 
    LegalAuthoritySourceCode != "impt",
    LegalAuthoritySourceCode != "invo",
    LegalAuthoritySourceCode != "aqua"
  ) |> 
  group_by(
    BatchYear, LandingMonth,
    CatchAreaCode, CatchAreaDescription,
    FisherTypeDescription, GearCode
  ) |> 
  summarize(rc = sum(ReportedCount), .groups = "drop") |>  #server-side '.group = "drop"' not working; adds a new field "group" and retains groups
  collect() |> 
  mutate(
    across(contains("AreaCode"), str_trim),
    gear = if_else(GearCode %in% c(10,41), "line", "net"),
  ts = case_when(
    LandingMonth < 7 ~ 1,
    LandingMonth == 7 ~ 2,
    LandingMonth == 8 ~ 3,
    LandingMonth == 9 ~ 4,
    LandingMonth > 9 ~ 5
    )
  )

DBI::dbDisconnect(con_ft)

rm(con_ft)

saveRDS(ft_pull, "temp_ft_pull.rds")
```

```{r}
ft_pull <- readRDS("temp_ft_pull.rds")

ft_pull |> 
  #distinct(CatchAreaCode, CatchAreaDescription, FisherTypeDescription, GearCode, gear) |> writexl::write_xlsx("temp_fishtix.xlsx")
  group_by(year = BatchYear, CatchAreaCode, CatchAreaDescription, FisherTypeDescription, gear, ts) |> 
  summarise(rc = sum(rc), .groups = "drop") 

mutate(
  FisheryID = case_when(
    ~ 34, #A1-Ast Trl	WA Area 1 & Astoria Troll
    ~ 35, #Area2Trl NT	WA Area 2 Non-Treaty Troll
    ~ 36, #Area2TrlTR	WA Area 2 Treaty Troll
    ~ 38, #WA Area 3 Non-Treaty troll
    ~ 39, #WA Area 3 Treaty troll
    ~ 42,	#A4/4BTrlNT	WA Area 4/4B Non-Treaty Troll
    ~ 43,	#A4/4BTrlTR	WA Area 4/4B Treaty Troll
    ~ 44, #A5-6C Trl	WA Area 5-6-6C Troll; all Treaty troll
    ~ 47, #WlpaBT Net	Willapa Bay & FW Trib Net; all 22-14, Non-treaty Drift Gillnet
    
    CatchAreaCode & FisherTypeDescription  ~ 50, #GryHbr Net	Grays Harbor Estuary Net; all NT drift gillnet
    
    CatchAreaCode & FisherTypeDescription  ~ 52, #LwCheh Net	Lower Chehalis R Net
    CatchAreaCode & FisherTypeDescription  ~ 55, #Hump R Net	Humptulips R Net
    CatchAreaCode & FisherTypeDescription  ~ 56, #UpCheh Net	Upper Chehalis R Net
    CatchAreaCode & FisherTypeDescription  ~ 63, #Quin R Net	Quinault R Net
    CatchAreaCode & FisherTypeDescription  ~ 68, #Queets Net	Queets R Net
    CatchAreaCode & FisherTypeDescription  ~ 71, #Quilly Net	Quillayute R Net; should this get the 770 Sol Duc R recs?
    CatchAreaCode & FisherTypeDescription  ~ 74, #Hoh R  Net	Hoh R Net
    CatchAreaCode & FisherTypeDescription  ~ 77, #Mak FW Net	Makah Freshwater Net
    CatchAreaCode & FisherTypeDescription ~ 79,	#A 4-4A Net	WA Area 4-4A Net
    CatchAreaCode & FisherTypeDescription  ~ 80, #A4B6CNetNT	WA Area 4B-5-6C Non-Treaty Net; not assigned 23-16 Set Gillnet, 23-52 Mixed Net
    CatchAreaCode & FisherTypeDescription  ~ 81, #A4B6CNetTR	WA Area 4B-5-6C Treaty Net; assigned 23-16 Set Gillnet, 23-52 Mixed Net
    CatchAreaCode & FisherTypeDescription  ~ 82, #Ar6D NetNT	6D Non-Treaty Net (Dungeness Bay & R); no FW net recs with "DUNGENESS" in name
    CatchAreaCode & FisherTypeDescription  ~ 83, #Ar6D NetTR	6D Treaty Net (Dungeness Bay & R); no FW net recs with "DUNGENESS" in name
    
    CatchAreaCode & FisherTypeDescription  ~ 84, #Elwha  Net	Elwha R Net
    CatchAreaCode & FisherTypeDescription ~ 85,	#WJDF T Net	West JDF Straits Trib Net
    CatchAreaCode & FisherTypeDescription ~ 86,	#EJDF T Net	East JDF Straits Trib Net
    CatchAreaCode & FisherTypeDescription  ~ 87, #A6-7ANetNT	WA Area 7-7A Non-Treaty Net
    CatchAreaCode & FisherTypeDescription  ~ 88, #A6-7ANetTR	WA Area 7-7A Treaty Net
    
    CatchAreaCode & FisherTypeDescription ~ # 96	A7BCDNetNT	WA Area 7B-7C-7D Non-Treaty Net
      CatchAreaCode & FisherTypeDescription ~ # 97	A7BCDNetTR	WA Area 7B-7C-7D Treaty Net
      CatchAreaCode & FisherTypeDescription ~ # 98	Nook R Net	Nooksack R Net
      CatchAreaCode & FisherTypeDescription ~ # 101	Ar 8 NetNT	WA Area 8 Non-Treaty Net (Skagit)
      CatchAreaCode & FisherTypeDescription ~ # 102	Ar 8 NetTR	WA Area 8 Treaty Net (Skagit)
      CatchAreaCode & FisherTypeDescription ~ # 103	Skag R Net	Skagit R Net
      CatchAreaCode & FisherTypeDescription ~ # 104	SkgR TsNet	Skagit River Test Net
      CatchAreaCode & FisherTypeDescription ~ # 105	SwinCh Net	Swinomish Channel Net
      CatchAreaCode & FisherTypeDescription ~ # 109	Ar8A NetNT	WA Area 8A Non-Treaty Net
      CatchAreaCode & FisherTypeDescription ~ # 110	Ar8A NetTR	WA Area 8A Treaty Net
      CatchAreaCode & FisherTypeDescription ~ # 111	Ar8D NetNT	WA Area 8D Non-Treaty Net (Tulalip Bay)
      CatchAreaCode & FisherTypeDescription ~ # 112	Ar8D NetTR	WA Area 8D Treaty Net (Tulalip Bay)
      CatchAreaCode & FisherTypeDescription ~ # 113	Stil R Net	Stillaguamish R Net
      CatchAreaCode & FisherTypeDescription ~ # 114	Snoh R Net	Snohomish R Net
      CatchAreaCode & FisherTypeDescription ~ # 119	Ar10 NetNT	WA Area 10 Non-Treaty Net (Seattle)
      CatchAreaCode & FisherTypeDescription ~ # 120	Ar10 NetTR	WA Area 10 Treaty Net (Seattle)
      CatchAreaCode & FisherTypeDescription ~ # 121	Ar10ANetNT	WA Area 10A Non-Treaty Net (Elliott Bay)
      CatchAreaCode & FisherTypeDescription ~ # 122	Ar10ANetTR	WA Area 10A Treaty Net (Elliott Bay)
      CatchAreaCode & FisherTypeDescription ~ # 123	Ar10ENetNT	WA Area 10E Non-Treaty Net (East Kitsap)
      CatchAreaCode & FisherTypeDescription ~ # 124	Ar10ENetTR	WA Area 10E Treaty Net (East Kitsap)
      CatchAreaCode & FisherTypeDescription ~ # 125	10F-G  Net	WA Area 10F-G Treaty Net (Lake Union)
      CatchAreaCode & FisherTypeDescription ~ # 126	Duwm R Net	Green/Duwamish R Net
      CatchAreaCode & FisherTypeDescription ~ # 130	Ar11 NetNT	WA Area 11 Non-Treaty Net (E/W Pass)
      CatchAreaCode & FisherTypeDescription ~ # 131	Ar11 NetTR	WA Area 11 Treaty Net (E/W Pass)
      CatchAreaCode & FisherTypeDescription ~ # 132	Ar11ANetNT	WA Area 11A Non-Treaty Net (Comm. Bay)
      CatchAreaCode & FisherTypeDescription ~ # 133	Ar11ANetTR	WA Area 11A Treaty Net (Comm. Bay)
      CatchAreaCode & FisherTypeDescription ~ # 134	Puyl R Net	Puyallup R Net
      CatchAreaCode & FisherTypeDescription ~ # 137	Ar13 NetNT	Area 13 Non-Treaty Net (So Puget Sound)
      CatchAreaCode & FisherTypeDescription ~ # 138	Ar13 NetTR	Area 13 Treaty Net (So Puget Sound)
      CatchAreaCode & FisherTypeDescription ~ # 139	Ar13CNetNT	Area 13C Non-Treaty Net (Chambers Bay)
      CatchAreaCode & FisherTypeDescription ~ # 140	Ar13CNetTR	Area 13C Treaty Net (Chambers Bay)
      CatchAreaCode & FisherTypeDescription ~ # 141	Ar13ANetNT	Area 13A Non-Treaty Net (Carr Inlet)
      CatchAreaCode & FisherTypeDescription ~ # 142	Ar13ANetTR	Area 13A Treaty Net (Carr Inlet)
      CatchAreaCode & FisherTypeDescription ~ # 143	Ar13DNetNT	Area 13D Non-Treaty Net
      CatchAreaCode & FisherTypeDescription ~ # 144	Ar13DNetTR	Area 13D Treaty Net
      CatchAreaCode & FisherTypeDescription ~ # 145	A13FKNetNT	Area 13F-13K Non-Treaty Net
      CatchAreaCode & FisherTypeDescription ~ # 146	A13FKNetTR	Area 13F-13K Treaty Net
      CatchAreaCode & FisherTypeDescription ~ # 147	Nisq R Net	Nisqually R Net
      CatchAreaCode & FisherTypeDescription ~ # 148	McAlls Net	McAllister Creek Net
      CatchAreaCode & FisherTypeDescription ~ # 153	1212BNetNT	Area 12-12B Hood Canal Non-Treaty Net
      CatchAreaCode & FisherTypeDescription ~ # 154	1212BNetTR	Area 12-12B Hood Canal Treaty Net
      CatchAreaCode & FisherTypeDescription ~ # 155	A9-9ANetNT	Area 9/9A Non-Treaty Net
      CatchAreaCode & FisherTypeDescription ~ # 156	A9-9ANetTR	Area 9/9A Treaty Net (On Res)
      CatchAreaCode & FisherTypeDescription ~ # 157	Ar12ANetNT	Area 12A Non-Treaty Net (Quilcene Bay)
      CatchAreaCode & FisherTypeDescription ~ # 158	Ar12ANetTR	Area 12A Treaty Net (Quilcene Bay)
      CatchAreaCode & FisherTypeDescription ~ # 159	A12CDNetNT	Area 12C-12D Non-Treaty Net (SE Hood Canal)
      CatchAreaCode & FisherTypeDescription ~ # 160	A12CDNetTR	Area 12C-12D Treaty Net (SE Hood Canal)
      CatchAreaCode & FisherTypeDescription ~ # 161	Skok R Net	Skokomish R Net
      CatchAreaCode & FisherTypeDescription ~ # 162	Quilcn Net	Quilcene R Net
      
  )
)
```


# CWTs

# Assignment