---
title: "rrCoho 2021"
author: "Dan.Auerbach@dfw.wa.gov"
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
output: 
  bookdown::html_document2:
    self_contained: true
    fig_caption: yes
    theme: flatly
    toc: yes
    toc_depth: 3
    toc_float: yes
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = FALSE, warning = FALSE, message = FALSE, fig.width = 9, fig.height = 9)

library("tidyverse")
library("gt")

if(grepl("apple", sessionInfo()$platform)){
  file_path <- list(
    escp = "~/T/DFW-Salmon Mgmt Modeling Team - General/Escapement files/Coho/fram_coho_escapement_2023.xlsx",
    crc_mdb = "~/T/DFW-Salmon Mgmt Modeling Team - General/Catch datasets/CRC/Sport Harvest Estimates 20221116.mdb",
    tocas = "~/T/DFW-Salmon Mgmt Modeling Team - General/PS Coho Run Reconstruction/2021/CohoRR_sthurner_Tocas_11-01-2023_14_38_41.csv",
    rmis_rec = "~/T/DFW-Salmon Mgmt Modeling Team - General/PS Coho Run Reconstruction/2021/rmis_recs_2019_2022.csv",
    rmis_all_rel = "~/T/DFW-Salmon Mgmt Modeling Team - General/PS Coho Run Reconstruction/2021/rmis_releases_all_coho_by2010_onward.csv",
    lu_xlsx = "~/O/code/framr/xlsx/lu_coho.xlsx"
  )
} else {
  file_path <-   list(
    escp = "T:/DFW-Salmon Mgmt Modeling Team - General/Escapement files/Coho/fram_coho_escapement_2023.xlsx",
    crc_mdb = "T:/DFW-Salmon Mgmt Modeling Team - General/Catch datasets/CRC/Sport Harvest Estimates 20221116.mdb",
    tocas = "T:/DFW-Salmon Mgmt Modeling Team - General/PS Coho Run Reconstruction/2021/CohoRR_sthurner_Tocas_11-01-2023_14_38_41.csv",
    rmis_rec = "T:/DFW-Salmon Mgmt Modeling Team - General/PS Coho Run Reconstruction/2021/rmis_recs_2019_2022.csv",
    rmis_all_rel = "T:/DFW-Salmon Mgmt Modeling Team - General/PS Coho Run Reconstruction/2021/rmis_releases_all_coho_by2010_onward.csv",
    lu_xlsx = "O:/code/framr/xlsx/lu_coho.xlsx"
  )
}

#fixed lookups from CRC, TOCAS, and RMIS to FRAM FisheryID and RMIS to PR_MU/StockID
lu <- map(
  set_names(readxl::excel_sheets(file_path$lu_xlsx))
  ,
  ~readxl::read_excel(file_path$lu_xlsx, sheet = .x)
  )
lu$crc_fram <- lu$crc_fram |> mutate(across(starts_with('FisheryID'), as.integer))
lu$tocas_fram <- lu$tocas_fram |> mutate(across(starts_with('FisheryID'), as.integer))

#ANNUAL lookup/flagging for allowed PR_MUs in CAs
#and whether to use CWTs
lu$ca_pr_mu_flagged <- readxl::read_excel("ca_pr_mu_flagged.xlsx")

data_in <- list()
rr <- list()
```

https://fisheriesservices.nwifc.org/fram-model-runs/preseason-fram-model-preparation/salmon-run-reconstruction-puget-sound/

# Escapement

 - expects/relies on current format of *fram_coho_escapement_YEAR.xlsx* file
 - reads 'dataset' sheet and wrangles to 'RRTerm' summarization by PR + PR_MU
 - replacement needs to maintain PR & PR_MU fields per escapement estimate value

```{r read_escp}
data_in$escp <- readxl::read_excel(
  path = file_path$escp,
  sheet = "dataset"
)|> 
  group_by(year, RRTerm_PR, RRTerm_PR_MU) |> 
  summarise(escp = sum(escp_val, na.rm = T), .groups = "drop") |> 
  mutate(
    PR_MU = paste(RRTerm_PR, RRTerm_PR_MU, sep = "_"),
    across(c(year, escp), as.integer)
    )
```

# Sport catches from CRC

Refactored from *CohoFRAM_PostSeasonwMZ_RR_SportFisheryInputs_111021.R*
  - Persisted removal of AreaCode == 192
  - Persisted Timestep based on `catchstatmonth` ignoring start/end dates outside single month
  - Persisted CRC~FRAM LU assignment in `framr`-based LU
  - Then assigns RRTerm CA from FRAM FisheryID
  - Catches only summed from FRAM timestep 3+4+5 FW or 4+5 Marine (Aug+Sep+Oct-Nov).

```{r read_crc_coho_osx}
data_in$crc <- dplyr::left_join(
  system2("mdb-export", args = paste(str_replace_all(file_path$crc_mdb, " ", "\\\\ "), "Catch"), stdout = T) |> I() |> readr::read_csv()
  ,
  system2("mdb-export", args = paste(str_replace_all(file_path$crc_mdb, " ", "\\\\ "), "Area"), stdout = T) |> I() |> readr::read_csv()
  ,
  by = "AreaID") |> 
  dplyr::rename_with(.fn = tolower) |> 
  filter(species == "Coho", areacode != "192") |>
  mutate(
    area_code = str_pad(areacode, width = 2, pad = "0"),
    dplyr::across(ends_with("date"), ~as.Date(., format = "%m/%d/%y")),
    catchstatmonth = if_else(is.na(catchstatmonth), as.integer(format(catchperiodstartdate, '%m')), as.integer(catchstatmonth))
    ) |>
  group_by(area_code, areaname, year = catchyear, catchstatmonth) |> 
  summarise(catchest = sum(catchest), .groups = "drop") |> 
  mutate(
    m = factor(month.abb[catchstatmonth], levels = month.abb),
    ts = case_when(
      m %in% month.abb[1:6] ~ 1,
      m == "Jul" ~ 2,
      m == "Aug" ~ 3,
      m == "Sep" ~ 4,
      m %in% month.abb[10:12] ~ 5)
    )
```

```{r read_crc_coho, eval=FALSE}
db_con <- DBI::dbConnect(
  drv = odbc::odbc(),
  .connection_string = paste0(
    "Driver={Microsoft Access Driver (*.mdb, *.accdb)};DBQ=",
    file_path$crc_mdb,
    ";"))

data_in$crc <- dplyr::left_join(
  dplyr::collect(dplyr::tbl(db_con, "Catch")) |> 
    dplyr::mutate(dplyr::across(ends_with("Date"), ~as.Date(., format = "%m/%d/%Y"))) 
  , 
  dplyr::collect(dplyr::tbl(db_con, "Area"))
  ,
  by = "AreaID") |> 
  dplyr::rename_with(.fn = tolower) |> 
  filter(species == "Coho", areacode != "192") |> 
  mutate(
    area_code = str_pad(areacode, width = 2, pad = "0"),
    catchstatmonth = if_else(is.na(catchstatmonth), as.integer(format(catchperiodstartdate, '%m')), catchstatmonth)
    ) |>
  group_by(area_code, areaname, year = catchyear, catchstatmonth) |> 
  summarise(catchest = sum(catchest), .groups = "drop") |> 
  mutate(
    m = factor(month.abb[catchstatmonth], levels = month.abb),
    ts = case_when(
      m %in% month.abb[1:6] ~ 1,
      m == "Jul" ~ 2,
      m == "Aug" ~ 3,
      m == "Sep" ~ 4,
      m %in% month.abb[10:12] ~ 5)
    )

DBI::dbDisconnect(db_con)

```

```{r data_in_crc_ca}
#maintaining FW 3+4+5, M 4+5 per AHB, but would prefer not to exclude pre-Aug catch on basis of 'dip in' concerns
#no idea how CWT_Flag, Cat_Flag, Type_Calc are used
data_in$crc_ca <- data_in$crc |> 
  left_join(select(lu$crc_fram, -FisheryID_alt), by = "area_code") |> 
  drop_na(FisheryID) |> 
  inner_join(lu$fram_ca, by = "FisheryID") |> 
  drop_na(RRTermType) |> 
  filter(ts > 2) |> 
  group_by(year, CA_Number, CA_Short_Name, RRTermType, ts) |> 
  summarise(catchest = sum(catchest), .groups = "drop") |> 
  pivot_wider(names_from = ts, values_from = catchest, values_fill = 0) |> 
  mutate(
    catch = case_when(
      RRTermType == "FW" ~ `3` + `4` + `5`,
      RRTermType == "M" ~ `4` + `5`
    )
  )
```

# Commercial catches from TOCAS

Refactored from *CohoFRAM_PostSeason_RR_CommCatchInputs_MB121621*

>TO QUERY RAW DATA (http://access.nwifc.org/webapps/index.asp)
>Biological Reports
>TOCAS/WAFT
>Breaks: SpeciesName, Fishery, Gear, GearName, Catch Area, Disposition, Landing Date, Tribe Name.
>Select - TOCAS Filled with WAFT Data
>Values:  Select - Units
>Criteria:
> Species Selected =  
> 004 - COHO
> 044 - COHO AQUACULTURE (Note: no results, but keep in query to see if any show-up....)
> (Do not include 874 - COHO EGGS)
> Tribes Selected = ALL
> Gears Selected = ALL
> Areas Selected = ALL
> Disposition Selected = ALL
> Dealers Selected = ALL
> Modify dates as needed

```{r read_tocas}
data_in$tocas <- read_csv(file_path$tocas) |> 
  rename_with(~str_remove_all(str_squish(.), " ")) |> 
  drop_na(Units, FisherType) |> 
  filter(Disposition %in% c("C&SF", "COMM", "ORGN", "TEST","TKHM")) |> 
  mutate(
    #landing_date = as.Date(Landing_Date, format = "%m/%d/%Y"),
    landing_date = as.Date(CatchDate, format = "%m/%d/%Y"),
    month = lubridate::month(landing_date),
    year = lubridate::year(landing_date),
    ts = case_when(
      month %in% 1:6 ~ 1,
      month == 7 ~ 2,
      month == 8 ~ 3,
      month == 9 ~ 4,
      month %in% 10:12 ~ 5)
  )
```

```{r data_in_tocas_ca}
data_in$tocas_ca <- data_in$tocas |> 
  #group_by(year, ts, Fishery, TribeName, Gear, Disposition, Catch_Area) |> 
  group_by(year, ts, FisherType, TribeName, Gear, Disposition, CatchArea) |> 
  summarise(catch = sum(Units), .groups = "drop") |> 
  mutate(TribeName = if_else(TribeName %in% c("QUINAULT - 18", "CHEHALIS - 02"), TribeName, NA_character_)) |> 
  left_join(
    lu$tocas_fram |> separate_rows(Disposition) |> separate_rows(Gear) |> mutate(Gear = as.integer(Gear)),
    by = c("FisherType", "TribeName", "Gear", "Disposition", "CatchArea")
  ) |> 
  drop_na(FisheryID) |> 
  inner_join(lu$fram_ca, by = "FisheryID") |> 
  drop_na(RRTermType) |> 
  filter(ts > 2) |> 
  group_by(year, CA_Number, CA_Short_Name, RRTermType, ts) |> 
  summarise(catch = sum(catch), .groups = "drop") |> 
  arrange(year, CA_Number, ts) |> 
  pivot_wider(names_from = ts, values_from = catch, values_fill = 0) |> 
  mutate(
    catch = case_when(
      RRTermType == "FW" ~ `3` + `4` + `5`,
      RRTermType == "M" ~ `4` + `5`
    )
  )
```

## combine

```{r data_in_catch}
data_in$catch <- bind_rows(
  data_in$crc_ca |> select(year, CA_Number, CA_Short_Name, RRTermType, catch),
  data_in$tocas_ca |> select(year, CA_Number, CA_Short_Name, RRTermType, catch)
)
```


# CWT recoveries

Refactored from MB scripts & SFund fishery & stock mapping

  - *CohoRR_CWT_PostProcess_FisheryMethod_MB121621* assigning recoveries to FRAM fisheries
  - *CohoRR_CWT_PostProcess_StockMethod_PEFCalcs_CWTForecast_MB010322_SEFMethod* assigning post-fishery wrangled recoveries to stocks and calc PEFs

MB escapement separating out C&S, so `fishery %in% c(50:54,57:59)`, excluding RMIS 55 & 56

Query from 'recoveries by tag code' (https://www.rmis.org/cgi-bin/queryfrm.mpl?Table=recoveriesbytagcode&tag_status=1&Version=4.1)
Tag Status == 1, Species == 2 (coho), Recovery Year = ...
User list of fields to paste into "User List" popup:
> sample_type, brood_year, tag_code, recovery_date, recovery_location_code, fishery, gear, estimated_number

```{r rmis_rec_rel}
# readr::read_csv("https://www.rmis.org/reports/CSV18307.txt") |>
#   write_csv("~/T/DFW-Salmon Mgmt Modeling Team - General/PS Coho Run Reconstruction/2021/rmis_recs_2019_2022.csv")

rmis_rec_rel <- left_join(
  read_csv(file_path$rmis_rec) |> 
    filter(
      sample_type != 5,
      (fishery < 50 | fishery %in% 55:56 | fishery > 59)
    )
  ,
  read_csv(file_path$rmis_all_rel) |> 
    select(
      tag_code = tag_code_or_release_id,
      brood_year, last_release_date,
      hatchery_location_name,
      stock_location_name,
      rearing_type,
      release_location_code, release_location_name, 
      cwt_1st_mark, #cwt_1st_mark_count, 
      cwt_2nd_mark, #cwt_2nd_mark_count, 
      non_cwt_1st_mark, #non_cwt_1st_mark_count, 
      non_cwt_2nd_mark #, non_cwt_2nd_mark_count
    )
  ,
  by = c("tag_code", "brood_year")
  ) |> 
  mutate(
    rec_date = as.Date(as.character(recovery_date), format = "%Y%m%d"),
    rec_year = lubridate::year(rec_date), 
    rec_year = if_else(is.na(rec_year) & nchar(as.character(recovery_date)) == 4,
                       as.integer(recovery_date),
                       as.integer(rec_year)),
    rec_month = lubridate::month(rec_date),
    rec_age = rec_year - brood_year,
    ts = case_when(
      rec_month %in% 1:6 ~ 1,
      rec_month == 7 ~ 2,
      rec_month == 8 ~ 3,
      rec_month == 9 ~ 4,
      rec_month %in% 10:12 ~ 5),
    fishery_single = floor(fishery/10)
  ) |> 
  tibble::rowid_to_column("uid") 
```

```{r rmis_to_fram_fish}
#first declare temp object of only key fields
rmis_rec_rel_to_map <- select(.data = rmis_rec_rel, uid, recovery_location_code, fishery_single)

#now overwrite as split-then-bind pattern on Num_Chars
#per AHB request, added explicit right string padding to specified string length
#even when actual strings in RMIS and LU are/use fewer char
rmis_rec_rel_to_map <- map_df(
  sort(unique(lu$rmis_fram_fishery$Num_Chars)),
  ~inner_join(
    rmis_rec_rel_to_map |> 
      mutate(
        PSC_Code = str_sub(recovery_location_code, 1, .x) |> 
          str_pad(width = .x, side = "right")
        )
    ,
    lu$rmis_fram_fishery |> 
      filter(Num_Chars == .x) |> 
      mutate(
        PSC_Code = str_pad(PSC_Code, width = .x, side = "right")
        )
    ,
    by = c("PSC_Code", "fishery_single")
  )
)

#now rejoin to full dataset, after making FisheryID distinct per UID
rmis_rec_rel <- left_join(
  rmis_rec_rel, 
  #split out any multiple-mapped, make distinct per UID and rebind
  bind_rows(
    #records that map to a single fishery
    anti_join(
      rmis_rec_rel_to_map
      ,
      rmis_rec_rel_to_map |> count(uid) |> filter(n>1) |> select(uid)
      , by = "uid"
      ) |> 
      select(uid, FisheryID)
    ,
    #MAY BE 0 ROWS records that map to multiple fisheries
    semi_join(
      rmis_rec_rel_to_map
      ,
      rmis_rec_rel_to_map |> count(uid) |> filter(n>1) |> select(uid)
      ,
      by = "uid"
      ) |> 
      group_by(uid) |> 
      slice_max(Num_Chars, n = 1, with_ties = F) |> 
      ungroup() |> 
      select(uid, FisheryID)
  )
  ,
  by = "uid"
  )

rm(rmis_rec_rel_to_map)

# #unmapped recoveries
# rmis_rec_rel |> filter(is.na(FisheryID)) |> count(recovery_location_code) |> print(n=100)
# #bad dates Indy 
# rmis_rec_rel |> filter(is.na(rec_date)) |> count(recovery_location_code) |> print(n=100)

```

Now assign FRAM StockID, limiting to marked, age 3, rearing type H or M

```{r rmis_rec_rel_to_fram_pr_mu}
rmis_rec_rel <- rmis_rec_rel |> 
  drop_na(FisheryID, rec_date, estimated_number) |> 
  filter(
    rec_age == 3,
    between(as.integer(cwt_1st_mark), 5000, 6000),
    rearing_type %in% c("H","M")
    ) |>
  left_join(lu$rmis_fram_pr_mu, by = "release_location_name") |> 
  drop_na(StockID, PR_MU)
```

```{r data_in_cwt}
data_in$cwt <- rmis_rec_rel |> 
  inner_join(lu$fram_ca, by = "FisheryID") |> 
  drop_na(RRTermType) |> 
  filter(ts > 2) |> 
  group_by(
    year = rec_year, ts,
    CA_Number, CA_Short_Name, RRTermType,
    PR_Number, PR_MU_Number, PR_MU, MU_Short_Name) |> 
  summarise(est_num = sum(estimated_number), .groups = "drop") |> 
  arrange(year, CA_Number, ts) |> 
  pivot_wider(names_from = ts, values_from = est_num, values_fill = 0) |> 
  mutate(
    est_num = case_when(
      RRTermType == "FW" ~ `3` + `4` + `5`,
      RRTermType == "M" ~ `4` + `5`
    ),
    #MB has HC fisheries as all 3+4+5
    est_num = if_else(
      between(CA_Number, 700, 756),
      `3` + `4` + `5`,
      est_num
      )
    ,`345` = `3` + `4` + `5`
  )
```

# PEF calcs

Divides the total releases by the tagged and marked.

(cwt_1st/2nd_mark_count + non_cwt_1st/2nd_mark_count) / cwt_1st/2nd_mark_count

Confirmed with AHB that we want to build ratio from tagged+marked only, not including UM+tagged (as when cwt_2nd_mark==0000 and cwt_2nd_mark_count > 0)...because only examining marked recoveries (and tagged by def of being recovered).

This first calcs per-tag_code total ("numerator") and marked+tagged ("denominator"), before then summing both per PR_MU to match MB code.

```{r rmis_rel_all}
# # #reran 2010-onward all releases
# # WHERE species = '2'
# # AND   brood_year IN (2010,2011,2012,2013,2014,2015,2016,2017,2018,2019,2020,2021,2022)
# rmis_rel_all <- readr::read_csv("https://www.rmis.org/reports/CSV1607.txt") 
# readr::write_csv(rmis_rel_all, "rmis_releases_all_coho_by2010_onward.csv")

rmis_rel_all <- readr::read_csv(file_path$rmis_all_rel) |> 
  mutate(
    last_release_date_year = lubridate::year(as.Date(as.character(last_release_date), format = "%Y%m%d")),
    last_release_date_year = if_else(
      is.na(last_release_date_year) & nchar(as.character(last_release_date)) == 4,
      as.integer(last_release_date),
      as.integer(last_release_date_year))
  ) |> 
  # #this creates some NAs for dates of format YYYYMM, but these appear to be "!nnn..." codes for non-tagged groups except for 211071 which is totally uninformative
  # filter(is.na(last_release_date_year)) |> count(str_sub(tag_code_or_release_id, 1,2))
  select(
    tag_code = tag_code_or_release_id, 
    related_group_id,
    brood_year, last_release_date_year, last_release_date,
    hatchery_location_name,
    stock_location_name,
    rearing_type,
    release_location_code, release_location_name, 
    cwt_1st_mark, cwt_1st_mark_count, 
    cwt_2nd_mark, cwt_2nd_mark_count, 
    non_cwt_1st_mark, non_cwt_1st_mark_count, 
    non_cwt_2nd_mark, non_cwt_2nd_mark_count,
    tagged_adclipped, tagged_unclipped, 
    untagged_adclipped, untagged_unclipped, untagged_unknown
    ) |> 
  tibble::rowid_to_column("uid")
```

```{r data_in_pef}
# #MB filters on rel_age==2 (constructing 'Match4' obj)
# Match2$rel_age = Match2$last_release_date_year - Match2$brood_year
# #but then groups on Run_ID (corresponding to recovery/fishing year?)
# Match4$Run_ID = (Match4$brood_year + 3)
# # but this seems like it potentially removes relevant releases?
# rmis_rel_all |> filter(tag_code == "!142017UH001")

data_in$pef <- rmis_rel_all |> 
  drop_na(last_release_date_year, release_location_name) |>
  filter(
    rearing_type %in% c("H","M"), #drop 'W', only a single 'M' in 2010onward file
    last_release_date_year - brood_year == 2
  ) |> 
  mutate(
    year = brood_year + 3,
    rel_sum = tagged_adclipped + tagged_unclipped + untagged_adclipped + untagged_unclipped + untagged_unknown,
    #rel_ad = tagged_adclipped + untagged_adclipped,
    rel_adcwt = tagged_adclipped
  ) |> 
  left_join(lu$rmis_fram_pr_mu, by = "release_location_name") |> 
  drop_na(StockID, PR_MU) |> 
  group_by(year, StockID, PR_MU) |> 
  summarise(
    across(c(starts_with("rel_"), contains("agged")), sum),
    #pef_ad = rel_sum / rel_ad,
    pef_adcwt = rel_sum / rel_adcwt,
    .groups = "drop"
  )

```

# Run reconstruction 

```{r shared_intermediates}
#potential PR_MUs in relevant CAs, now with both HR_Flag and CWT_Flag
rr$pr_ca_mu <- lu$ca_pr_mu_flagged |> 
  filter(HR_Flag == 1) |> 
  select(year, PR_Number, CA_Number, CA_Short_Name, PR_MU, MU_Short_Name, HR_Flag, CWT_Flag, MSF_Flag)

#expanded CWT estimated_number values
rr$cwt_pef <- data_in$cwt |> 
  select(year, CA_Number, PR_MU, est_num) |> 
  inner_join(
    rr$pr_ca_mu |> 
      filter(CWT_Flag==1) |> 
      select(year, CA_Number, PR_MU, CWT_Flag)
    ,
    by = c("year","CA_Number", "PR_MU")
    ) |> 
  left_join(data_in$pef |> select(year, PR_MU, pef_adcwt), by = c("year", "PR_MU")) |> 
  mutate(
    #Tulalip one-off adjustment per MB spreadsheet approach of matching target provided by Diego H
    est_num = if_else(year == 2021 & CA_Number == 583 & PR_MU == "3_3", 3827, est_num),
    cwt_pef = est_num * pef_adcwt
    )


#original catch values before deducting expanded CWT-catch
rr$catch <- data_in$catch |>
  semi_join(rr$pr_ca_mu, by = c("year", "CA_Number"))
##for 2020 testing against MB
rr$catch <- rr$catch |> 
  mutate(catch = if_else(year ==2020 & CA_Number == 563, 13357, catch))

#catch values after deducting total CWT-catch summed across relevant PR_MUs
rr$catch_less_cwt <- rr$catch |> 
  left_join(
    rr$cwt_pef |> 
      group_by(year, CA_Number) |> 
      summarise(cwt_pef_sum = sum(cwt_pef), .groups = "drop")
    ,
    by = c("year", "CA_Number")
  ) |> 
  mutate(catch_less_cwt = catch - cwt_pef_sum) 


#relevant escapement
rr$escp <- data_in$escp |> 
  select(year, PR_MU, escp) |> 
  semi_join(rr$pr_ca_mu, by = c("year", "PR_MU"))

#begin run size as escapement
rr$run_size <- rr$escp |> 
  mutate(rs = as.numeric(escp))

```

```{r loop_de_loop}
if(any(grepl("pr_temp", ls()))) { rm(pr_temp)}

rr$out <- tibble(
  year = numeric(),
  PR_Number = numeric(),
  CA_Number = numeric(),
  CA_Short_Name = character(),
  PR_MU = character(), 
  MU_Short_Name = character(),
  catch_pr_mu = numeric()
)

for (pr_num in 1:6){
  #sequential fisheries to evaluate
  ca_seq <- rr$pr_ca_mu |> 
    filter(PR_Number == pr_num) |> 
    pull(CA_Number) |> unique() |> sort(decreasing = T)

  #calc first fishery/CA outside of CA-for-loop
  pr_temp <- rr$pr_ca_mu |> 
    filter(PR_Number == pr_num, CA_Number == ca_seq[1]) |> 
    left_join(rr$run_size, by = c("year", "PR_MU")) |> 
    left_join(rr$catch_less_cwt, by = c("year", "CA_Number", "CA_Short_Name")) |> 
    left_join(rr$cwt_pef |> select(year, CA_Number, PR_MU, cwt_pef), by = c("year", "CA_Number", "PR_MU")) |> 
    group_by(year, PR_Number, CA_Number) |> 
    mutate(
      #sum over MUs in the CA not defined by CWTs
      rs_tot = sum(rs[is.na(cwt_pef)]),
      rs_pct = if_else(is.na(cwt_pef), rs / rs_tot, 0),
      catch_to_split = if_else(is.na(catch_less_cwt), catch, catch_less_cwt),
      catch_pr_mu = if_else(
        is.na(cwt_pef),
        catch_to_split * rs_pct,
        cwt_pef
        ) |> 
        replace_na(0),
      rs = rs + catch_pr_mu
    ) |> 
    ungroup()

  #overwrite with newly-catch-augmented RS
  rr$run_size <- rows_upsert(
    rr$run_size,
    pr_temp |> select(year, PR_MU, rs),
    by = c("year", "PR_MU"))
  #preserve
  rr$out <- rows_upsert(
    rr$out,
    pr_temp |>
      select(year, PR_Number, CA_Number, CA_Short_Name,
             PR_MU, MU_Short_Name, catch_pr_mu),
    by = c("year","PR_Number","CA_Number","CA_Short_Name",
           "PR_MU","MU_Short_Name"))
  
  #now cycle remaining CAs in the PR
  for (ca in ca_seq[-1]) {
    pr_temp <- rr$pr_ca_mu |> 
      filter(PR_Number == pr_num, CA_Number == ca) |> 
      left_join(rr$run_size, by = c("year", "PR_MU")) |> 
      left_join(rr$catch_less_cwt, by = c("year", "CA_Number", "CA_Short_Name")) |> 
      left_join(rr$cwt_pef |> select(year, CA_Number, PR_MU, cwt_pef), by = c("year", "CA_Number", "PR_MU")) |> 
      group_by(year, PR_Number, CA_Number) |> 
      mutate(
        #sum over MUs in the CA not defined by CWTs
        rs_tot = sum(rs[is.na(cwt_pef)]),
        rs_pct = if_else(is.na(cwt_pef), rs / rs_tot, 0),
        catch_to_split = if_else(is.na(catch_less_cwt), catch, catch_less_cwt),
        catch_pr_mu = if_else(
          is.na(cwt_pef),
          catch_to_split * rs_pct,
          cwt_pef
        ) |> 
          replace_na(0),
        rs = rs + catch_pr_mu
      ) |> 
      ungroup()
    #pr_temp #dev/testing
    
    #overwrite with newly-catch-augmented RS
    rr$run_size <- rows_upsert(
      rr$run_size,
      pr_temp |> select(year, PR_MU, rs),
      by = c("year", "PR_MU"))
    #preserve
    rr$out <- rows_upsert(
      rr$out,
      pr_temp |>
        select(year, PR_Number, CA_Number, CA_Short_Name,
               PR_MU, MU_Short_Name, catch_pr_mu),
      by = c("year","PR_Number","CA_Number","CA_Short_Name",
             "PR_MU","MU_Short_Name"))
    
  } #end CA-for-loop

} #end PR-for-loop

rm(pr_temp)
```

```{r}
rr$out |> 
  arrange(year, PR_Number, CA_Number, as.integer(str_sub(PR_MU, 3, 10))) |> 
  left_join(rr$escp, by = c("year", "PR_MU")) |> 
  unite("ca", starts_with("CA_")) |> 
  #filter(year==2020) |> 
  split(~PR_Number) |> 
  map(
    ~.x |> 
      mutate(catch_pr_mu = round(catch_pr_mu)) |> 
      pivot_wider(names_from = ca, values_from = catch_pr_mu)
  ) |> 
  c(rr) |> 
  writexl::write_xlsx("~/T/DFW-Salmon Mgmt Modeling Team - General/PS Coho Run Reconstruction/2021/temp_qaqc_2021_Jan19.xlsx")

```
